### 2021-09-09 manuscript/synthetic_data.tex
finish application to synthetic data

Our convolutional equivalent layer method requires a regular data grid located on a 
horizontal and flat observation surface.
Here, we evaluate the performance of our method by applying it to simulated airborne magnetic 
surveys formed by
i) a regular data grid on a flat surface;
ii) irregular data grids on a flat surface; and 
iii) regular data grid on an undulating surfaces.
Note that the simulated surveys in (ii) and (iii) violate the premises of our method. 
The simulated airborne magnetic surveys and the corresponding results 
are illustrated in Figures \ref{fig:synthetic_data_comparison_v2}, 
\ref{fig:synthetic_residuals_convergence_comparison_v2} and 
\ref{fig:synthetic_upward_residuals_comparison_v2}.

The upper and middle rows in Figure \ref{fig:synthetic_data_comparison_v2} show, respectively, 
the simulated flight patterns and noise-corrupted total-field anomalies of the airborne magnetic 
surveys. The lower row in Figure \ref{fig:synthetic_data_comparison_v2} shows the true 
upward-continued total-field anomalies at $z = -1, \, 300$ m.

All magnetic data (middle and lower rows in Figure \ref{fig:synthetic_data_comparison_v2}) 
are produced by the same three synthetic bodies: two prisms and one sphere with 
constant total-magnetization vector having inclination, declination and intensity of 
$0^{\circ}$, $45^{\circ}$, and $2.8284$ A/m, respectively. 
The simulated main geomagnetic field has inclination and declination of $10^{\circ}$ and $37^{\circ}$,
respectively.

PAREI AQUI

The  three rows in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}  show the data residuals 
obtained by using the classical method (the upper row), the data residuals obtained by using the
convolutional equivalent layer (the middle row), and the convergence curve of the convolutional equivalent layer (the lower row).

From now on, we call "the convolutional equivalent layer" as "our method" and we use the phrase "data residuals" to define the difference between the observed (middle row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted data (not shown) obtained by the classical method or by the convolutional equivalent layer (our method).

%% Regular grid

Figure \ref{fig:synthetic_data_comparison_v2}a shows a regular grid of  $100 \times 50$ observation points in the $x$- and $y$-directions, totaling  $N = 5,\, 000$ observation points. 
The noise-corrupted total-field anomaly (Figure \ref{fig:synthetic_data_comparison_v2}) is calculated at $900$ m height. 
The data residuals using the classical method (equation \ref{eq:estimated-p-parameter-space}) are shown in the upper panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a, 
with mean of $0.3627$ nT and standart deviation of $0.2724$ nT.
This process took $17.10$ seconds.
Using our method, the running time to estimate the data residuals (the middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a), with mean of $0.5223$ nT and standart deviation of $0.4323$ nT. The processing time was $0.18$ seconds.
Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a (lower panel) shows the convergence of our method. The Euclidean norm of the data residuals decreases as expected when the
convergence criterion was satisfied, close to iteration 50.

This result shows that, in practice, it is not necessary to run the conjugate gradient least square method at $N$ iterations to get an exactly solution.
Actually, the exactly solution  would never occur due to roundoff errors.
Hence, by setting the convergence to  $N$ iterations besides being unnecessary it also demands large computer processing time, even in this synthetic test with a small layer 
($N = 5,\, 000$ equivalent sources).

%======================================================================================
\subsection*{Tests with data on irregular grids}
%======================================================================================

As shown in the methodology, a regular grid of observation points is needed to arise the BTTB matrix. 
Here, we show the results when our method is applied directly to irregular grids of $N = 5 \, 000$ observation points. 
First, we start from the  regular grid of $100 \times 50$ observation points, shown in Figure 
\ref{fig:synthetic_data_comparison_v2}a,  with a grid spacing of $\Delta x$ of $101.01$ m along the $x$-axis and $\Delta y$ of $163.265$ m along the $y$-axis. 
Next, the $x$- and $y$-coordinates of the observations were also contaminated with additive pseudorandom Gaussian noise with zero mean and standard deviations of $20\%$ and $30\%$ of the $\Delta x$ and $\Delta y$ spacing.

%% irregular grid with 20%

Figure \ref{fig:synthetic_data_comparison_v2}b (upper panel) shows an irregular grid with uncertainty  of $20\%$ along both $x$- and $y$-directions of the observation points. 
Hence, the $x$- and $y$-coordinates of the observations shown in the regular grid (upper panel in Figure
\ref{fig:synthetic_data_comparison_v2}a)  were corrupted with sequences of pseudorandom Gaussian noise 
having zero means and standard deviations of $20.2$ m and $32.65$ m, respectively.
The noise-corrupted total-field anomaly (middle panel in Figure \ref{fig:synthetic_data_comparison_v2}b) is calculated on this irregular grid and on a flat observation surface at $900$ m height.

Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b shows that the data residuals using the classical approach (upper panel) yield a good data fit with mean of $0.3630$ nT and standart deviation of $0.2731$ nT. 
Using our method, the data residuals (middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b) also produced an acceptable data fitting with mean of  $0.7147$ nT and standart deviation of $0.5622$ nT. 
The  Euclidean norm of the data residuals obtained by our method 
(Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b) decreases as expected and close to iteration 50 congerves to a constant value.

%%  irregular grid with 30%

Figure \ref{fig:synthetic_data_comparison_v2}c (upper panel) shows an irregular grid with uncertainty  of $30\%$ along both $x$- and $y$-directions of the observation points.
Hence, Gaussian pseudorandom noise sequences with zero means and standard deviations of 
$30.3$ m and $48,98$ m were added, respectively, to the $x$- and $y$-coordinates of the observations shown in the regular grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}a), producing the simulated irregular grid shown in Figure \ref{fig:synthetic_data_comparison_v2}c.
Figure \ref{fig:synthetic_data_comparison_v2}c shows the noise-corrupted total-field anomaly 
(middle panel) calculated on the irregular grid (upper panel) and on a flat observation surface at $900$ m height.

Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c shows that the data residuals obtained by the classical approach (upper panel) produced an acceptable data fitting, having mean of $0.3634$ nT and standart deviation of $0.2735$ nT. 
Using our method, the data residuals (middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean of $0.9788$ nT and standart deviation of $0.7462$ nT produced a poor data fitting.
Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c shows the convergence analysis of our method.
Similarly to the previous results, in the begining of the iterations, the Euclidean norm of the data residuals obtained by our method decreases; however it starts increasing without achieving an invariance.
Hence, the convergence is not achieved.

%======================================================================================
\subsection*{Tests with data over an undulating observation surface}
%======================================================================================

Here, we simulate an airborne magnetic survey considering the same regular grid of $100 \times 50$ observation points shown in Figure  \ref{fig:synthetic_data_comparison_v2}a.
However, the observation points were no longer in a plane at $900$ m height, 
but they are over an undulating observation surface.
The next tests, the $z$-coordinates of the observations were contaminated with 
pseudorandom Gaussian noise mean of $- 900$ m and standard deviations of $5\%$ and $10\%$ of the $900$ m height.

%% Synthetic test with data over an undulating observation surface with uncertainty of $5\%$

Figure \ref{fig:synthetic_data_comparison_v2}d (upper panel) shows an uneven surface of observations where  the $z$-coordinates of the observations were corrupted with additive  pseudorandom Gaussian noise having mean of  $- 900$ m  and a standard deviation of $45$ m.
The middle panel in Figure \ref{fig:synthetic_data_comparison_v2}d shows the noise-corrupted total-field anomaly calculated on a regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates 
(upper panel in Figure  \ref{fig:synthetic_data_comparison_v2}a) and
over the undulating observation surface (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}d).

The data residuals either using classical approach 
(upper panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) or
using our method (middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) reveal acceptable data fitting.
Using the classical approach, the data residuals have mean of $0.3712$ nT 
and standart deviation of $0.2870$ nT.
Using our method, the data residuals have mean of $0.9542$ nT and standart deviation of $0.8943$ nT. 
Likewise,  Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d shows that the Euclidean norm of the data residuals, which were obtained by using our method, decreases up to the iteration 50  
and reaches an invariance in the subsequent iterations.

%% Synthetic test with data over an undulating observation surface with uncertainty of $10\%$

The upper panel in Figure \ref{fig:synthetic_data_comparison_v2}e shows an uneven surface of observations where  the $z$-coordinates of the observations were corrupted with additive pseudorandom Gaussian noise having mean of  $- 900$ m  and a standard deviation of $90$ m.
The noise-corrupted total-field anomaly calculated on a regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates (upper panel in Figure  \ref{fig:synthetic_data_comparison_v2}a) and
over the undulating observation surface (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}e)
is shown in Figure \ref{fig:synthetic_data_comparison_v2}e (middle panel).

By using the classical approach, the upper panel in 
Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e shows that the data residuals 
yielded a good data fitting, with  mean of $0.3865$ nT and standart deviation of $0.3216$ nT. 
By using our method,  the data residuals (middle panel in 
Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e) yielded a poor data  fitting with mean of $1.6109$ nT and standart deviation of $1.6231$ nT.
The convergence analysis (Figure\ref{fig:synthetic_residuals_convergence_comparison_v2}e)
reveals the inadequacy of our method in dealing with rugged  surface of observations, as 
the Euclidean norm of the data residuals decreases slower than previous tests.

Although our method is formulated to deal with magnetic observations measured on a regular grid, in 
the $x$- and $y$-directions, and on a flat surface, the synthetic results show that our method is 
robust in dealing either with irregular grids in the horizontal directions or with uneven surface.
However, the robustness of our method has limitations.
The performance limitation of our method depends on the degree of the 
departure of the $x$- and $y$-coordinates of the data from there corresponding coordinates on a regular grid
and from the amplitude of the undulating observation surface.
High departures of the $x$- and $y$-coordinates  from a regular grid and large variations in the data elevation ($z$-coordinates of the data) are associated with unacceptable data fittings (large data residuals) as shown the middle panels in Figures \ref{fig:synthetic_residuals_convergence_comparison_v2}c and \ref{fig:synthetic_residuals_convergence_comparison_v2}e, respectively.
However, the poor performance of our method in cases of irregular grid and uneven observation surface can be detected easily because, besides it leads to poor data fitting, it does not show an expected convergence as shown the lower panels in Figures \ref{fig:synthetic_residuals_convergence_comparison_v2}c  and \ref{fig:synthetic_residuals_convergence_comparison_v2}e.

@@

We performed the upward continuations of the noise-corrupted total-field anomalies 
(second row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
the classical method, the convolutional equivalent layer method (our method), and 
the classical approach in the Fourier domain.
The noise-free total-field anomalies produced by the synthetic sources at $z = -1, \, 300$ m 
(third row in Figure \ref{fig:synthetic_data_comparison_v2}) are called the true upward-continued total-field anomalies at $z = -1, \, 300$ m.

Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows the data residuals of the upward-continued total-field anomalies obtained by the classical method (first row), our method (second row) and the classical approach in the Fourier domain (third row).
The upward continuation by using the classical approach in Fourier domain consists in  
computing the Fourier transform of the total-field anomaly \citep[][ p. 317]{blakely1996}. 
From now on, we use the phrase "data residuals of the upward-continued total-field anomalies" to define the difference between the true upward-continued total-field anomalies (third row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted upward-continued total-field anomalies (not shown).

@@

Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows that the data residuals of the upward-continued total-field anomalies obtained by using the classical method (first row) and our method (second row) are, in most of the tests, similar to each other. 
One exception is the synthetic test with data over an undulating observation surface with uncertainty 
of $10\%$ shown in Figures \ref{fig:synthetic_data_comparison_v2}e and 
\ref{fig:synthetic_residuals_convergence_comparison_v2}e.
We can note that the absolute value of the data residuals of the upward-continued total-field anomalies produced by using our method (middle panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e) 
are $\approx 2.5$ times greater than those produced by the classical method 
(upper panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e).
However, we stress that the simulated undulating observation surface in this test  
(upper panel in Figure \ref{fig:synthetic_data_comparison_v2}e) varies in a broad range from $z = - 570$ m to about $z = -1,\, 230$ m; thus, this simulated airborne magnetic survey greatly violates the requirement 
of a flat observation surface demanded by our method.

@@

In contrast, the data residuals of the upward-continued total-field anomalies obtained by using the 
the classic Fourier approach (third row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2})
are, in most of the tests, approximately  $6$ times greater than those produced by the classical method 
(first  row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and $4$ times greater than those produced by our method (second row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}).
We can note that the maximum and minimum  values of the the data residuals of the upward-continued total-field anomalies obtained by using the the classic Fourier approach are located at the boundaries of the simulated area.

We call attention to the following aspects. 
In applying the classical method, our method, or the classical Fourier approach, we do not expand the data by using a padding function.
The data residuals (first and second rows in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2})
and the data residuals of the upward-continued total-field anomalies 
(Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) are fully shown  without removing the  edge effects at the borders of the simulated area. 
As pointed out in the methodology, the computational time required by our method is much lower than the one required by the classical method.
However, the computational time required by the classical Fourier approach is the lowest one.
Although, the classical Fourier approach is faster than our method, the upward-continued data exhibit strong border effects if no one padding function to expand the data was applied.

>>>>

Our convolutional equivalent layer method requires a regular data grid located on a 
horizontal and flat observation surface.
Here, we evaluate the performance of our method by applying it to simulated airborne magnetic 
surveys formed by
i) a regular data grid on a flat surface;
ii) irregular data grids on a flat surface; and 
iii) regular data grid on undulating surfaces.
Note that the simulated surveys in (ii) and (iii) violate the premises of our method.

%=======================================
\subsection*{Simulated airborne surveys}
%=======================================

The upper and middle rows in Figure \ref{fig:synthetic_data_comparison_v2} show, respectively, 
the simulated flight patterns and noise-corrupted total-field anomalies of the airborne magnetic 
surveys used in our tests. The lower row in Figure \ref{fig:synthetic_data_comparison_v2} shows 
the true upward-continued total-field anomalies at $z = -1, \, 300$ m.
All magnetic data (middle and lower rows in Figure \ref{fig:synthetic_data_comparison_v2}) 
are produced by the same three synthetic bodies: two prisms and one sphere with 
constant total-magnetization vector having inclination, declination and intensity of 
$0^{\circ}$, $45^{\circ}$, and $2.8284$ A/m, respectively. 
The simulated main geomagnetic field has inclination and declination of $10^{\circ}$ and $37^{\circ}$,
respectively.

%% regular grid on a flat surface

Figure \ref{fig:synthetic_data_comparison_v2}a shows the simulated airborne survey on
a regular grid of $100 \times 50$ observation points (totaling  $N = 5,\, 000$ observation points),
with a grid spacing of $\Delta x = 101.01$ m and $\Delta y = 163.265$ m along the
$x$- and $y$-axis, respectively.
The noise-corrupted total-field anomaly (middle panel) is calculated at $z = -900$ m, with a
pseudorandom Gaussian noise having null mean and standard deviation of $XXXX$ nT.

%% irregular grids on a flat surface

Figures \ref{fig:synthetic_data_comparison_v2}b and \ref{fig:synthetic_data_comparison_v2}c 
show the simulated surveys on irregular grids obtained by perturbing the horizontal coordinates
of the regular grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}a).
For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}b, the $x$ and $y$ coordinates 
are perturbed with sequences of pseudorandom Gaussian noises having null mean and standard deviations
equal to $20\%$ of the corresponding grid spacing, which results in
absolute values of $20.2$ m and $32.6$ m, along the $x$- and $y$-directions, respectively.
For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}c, the standard deviations
are equal to $30\%$ of the corresponding grid spacing, which results in absolute values of 
$30.3$ m and $49.0$ m along the $x$- and $y$-directions, respectively.
Their noise-corrupted total-field anomalies (middle panels in Figures 
\ref{fig:synthetic_data_comparison_v2}b and \ref{fig:synthetic_data_comparison_v2}c) are calculated 
on their corresponding irregular grids, on a flat observation surface at $z = -900$ m, 
with a pseudorandom Gaussian noise having null mean and standard deviation of $XXXX$ nT.

%% regular grid on undulating surfaces

Figures \ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e 
show the simulated surveys on the same regular grid shown in Figure 
\ref{fig:synthetic_data_comparison_v2}a (upper panel). The difference is that 
they are no longer on a flat, but on undulating surfaces.
For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}d, the $z$ coordinates 
of the undulating surface are defined by a sequence of pseudorandom Gaussian noise having mean 
$-900$ m and standard deviation equal to $5\%$ of $900$ m, which corresponds to $45$ m.
For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}e, the standard deviation 
is equal to $10\%$ of $900$ m, which corresponds to $90$ m.
The noise-corrupted total-field anomalies of these simulated surveys (middle panels in Figures 
\ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e) are calculated 
on their corresponding undulating surfaces (upper panels in Figures 
\ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e),
on the same regular grid shown in Figure \ref{fig:synthetic_data_comparison_v2}a,
with a pseudorandom Gaussian noise having null mean and standard deviation of $XXXX$ nT.

%% Regular grid
%======================================================================================
\subsection*{Tests with a regular data grid on a flat surface}
%======================================================================================

Figure \ref{fig:synthetic_residuals_convergence_comparison_v2} show the 
difference between the simulated (middle row in Figure \ref{fig:synthetic_data_comparison_v2})
and predicted data (not shown) obtained by using the classical (the upper row) and 
our method (the middle row). From now on, we designate this difference as data residuals. 
The lower row in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2} shows the 
convergence curve of our method.

The data residuals using the classical method (equation \ref{eq:classical-method})  
are shown in the upper panel of Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a, 
with mean $0.3627$ nT and standard deviation $0.2724$ nT. This process took $17.10$ seconds.
Using our method, the data residuals (the middle panel in Figure
\ref{fig:synthetic_residuals_convergence_comparison_v2}a) have mean $0.5223$ nT and standard
deviation $0.4323$ nT. In this case, however, the processing time was only $0.18$ seconds.
As expected, the Euclidean norm of the data residuals produced by our method 
(lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a) decreases 
and the convergence criterion is satisfied close to iteration $50$. 
This result shows that, in practice, our method converges way before $N$ iterations,
where $N$ is the number of observations.
Setting the convergence to $N$ iterations, besides being unnecessary, it also demands a larger 
computer processing time, even in this synthetic test with a small number 
of $N = 5,\, 000$ observations.

%======================================================================================
\subsection*{Tests with irregular data grids on a flat surface}
%======================================================================================

Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b shows the results obtained
with the irregular data grid perturbed by using $20\%$ of the regular grid spacing.
In this Figure we can see that the data residuals 
using the classical method (upper panel) yield a good data fit with mean $0.3630$ nT and standard
deviation $0.2731$ nT. 
Using our method, the data residuals (middle panel in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}b) also produced an acceptable data 
fitting with mean of  $0.7147$ nT and standart deviation of $0.5622$ nT. 
The Euclidean norm of the data residuals obtained by our method 
(lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b) decreases, 
as expected, and converges to a constant value close to iteration $50$.

Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b shows the results obtained
with the irregular data grid perturbed by using $30\%$ of the regular grid spacing.
This figure shows that the data residuals 
obtained by the classical method (upper panel) produced an acceptable data fitting, having mean 
$0.3634$ nT and standard deviation $0.2735$ nT. 
Using our method, the data residuals (middle panel in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $0.9788$ nT and 
standard deviation $0.7462$ nT produced a worse data fitting.
The convergence of our method (lower panel in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
similarly to the previous results, the Euclidean norm of the residuals decreases; however it starts
increasing without achieving an invariance. Hence, the convergence is not achieved.

\textbf{Alternative text} $\rightarrow$

Using our method, the data residuals (middle panel in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean (usar valor com a menor norma euclidiana) nT and 
standard deviation (usar valor com a menor norma euclidiana) nT also produced a good data fitting.
The convergence of our method (lower panel in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
similarly to the previous results, the Euclidean norm of the residuals decreases; however it starts
increasing without achieving an invariance. In this case, we have to stop the algorithm
before the iteration $N$. Note that this good result was obtained by using a very perturbed
data grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}c).

$\leftarrow$ \textbf{Alternative text}

%======================================================================================
\subsection*{Tests with regular data grid an undulating surfaces}
%======================================================================================

Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d shows the results obtained
with data on the undulating surface varying $5\%$ of $z = 900$ m.
In this case, the data residuals either using the classical method 
(upper panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) or
our method (middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) reveal
acceptable data fittings.
Using the classical method, data residuals have mean $0.3712$ nT and standard deviation $0.2870$ nT.
Using our method, they have mean $0.9542$ nT and standard deviation $0.8943$ nT. 
Likewise, the Euclidean norm of the data residuals produced by our method 
(lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) decreases up to 
iteration 50 and reaches an invariance in the subsequent iterations.

Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d shows the results obtained
with data on the undulating surface varying $10\%$ of $z = 900$ m.
By using the classical approach, the data residuals (upper panel in 
Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e) 
yielded a good data fitting, with mean $0.3865$ nT and standard deviation $0.3216$ nT. 
By using our method, the data residuals (middle panel in 
Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e) yielded a worse data fitting 
with mean $1.6109$ nT and standard deviation $1.6231$ nT.
The convergence curve (lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e)
reveals the inadequacy of our method in dealing with observations on rugged surfaces, as 
the Euclidean norm of the data residuals decreases slower than in previous tests. 
We stress that, in this test, the undulating surface (upper panel in Figure 
\ref{fig:synthetic_data_comparison_v2}e) varies in a broad range from $z = - 570$ m to about 
$z = -1,\, 230$ m. Thus, this simulated airborne magnetic survey greatly violates the requirement 
of a flat observation surface demanded by our method.

Although our method is formulated to deal with magnetic observations measured on 
a horizontally regular grid, on a flat surface, the results obtained with synthetic 
data show that our method is robust in dealing either with irregular grids in the 
horizontal directions or with uneven surfaces.
However, the robustness of our method has limitations.
The performance limitation of our method depends on the degree of 
departure of the (i) $x$- and $y$-coordinates from those of the closest 
regular grid and (ii) the $z$ coordinates from a constant value.
High departures in the $x$-, $y$, and $z$-coordinates lead to unacceptable 
data fittings (large data residuals), as shown the middle panels in Figures 
\ref{fig:synthetic_residuals_convergence_comparison_v2}c and
\ref{fig:synthetic_residuals_convergence_comparison_v2}e.

@@

We performed the upward continuations of the synthetic total-field anomalies 
(middle row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
the classical method, our convolutional equivalent layer method, and 
the classical approach in the Fourier domain,
which consists in computing the Fourier transform of the total-field anomaly 
\citep[e.g.,][ p. 317]{blakely1996}.

Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows the differences
between the true upward-continued total-field anomalies (lower row in Figure
\ref{fig:synthetic_data_comparison_v2}) and the predicted upward-continued total-field 
anomalies (not shown). We conveniently denote these differences as continuation
residuals.

@@

Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows that the continuation residuals 
obtained by using the classical method (upper row) and our method (middle row) are 
similar to each other in most of the tests.
One exception is the synthetic test with data over an undulating surface 
(Figures \ref{fig:synthetic_data_comparison_v2}e and 
\ref{fig:synthetic_residuals_convergence_comparison_v2}e), which greatly violates the 
requirement of a flat observation surface demanded by our method.
Note that the maximum absolute value of the continuation residuals produced by using our 
method (middle panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e) 
are $\approx 2.5$ times greater than those produced by the classical method 
(upper panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e).
Besides, they are generally concentrated at the boundaries of the study area.

@@

In contrast, the continuation residuals obtained by using the 
classical Fourier approach (lower row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2})
are, in most of the tests, approximately $6$ times greater than those produced by the classical method 
(upper row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and $4$ times greater than
those produced by our method (middle row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}).
Note that, similarly to our method, the maximum absolute values of the continuation residuals 
obtained by using the classical Fourier approach are located at the boundaries of the simulated area.
However, the values are significantly higher.

We call attention to the following aspects:
In applying the classical method, our method, or the classical Fourier approach, we do not expand 
the data by using a padding scheme.
The data residuals (upper and middle rows in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}) 
and the continuation residuals (Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) are
shown without removing the edge effects. 
The computational time required by our method is much lower than that required by the classical method
and has the same order of magnitude of that required by the classical Fourier approach.
However, the classical Fourier approach shows upward-continued data with strong border effects 
if no padding scheme is applied to expand the data.
